### 2019-10-16 README.Rmd
added another talking point
updated list of questions
updated readme

@@

- What names should I give to the diagnostic plots?
- Color themes for the paper?
- Metrics:
    - MSEE (mean squared explanation error?) versus locality metric which would need to be computed via the perturbations
    - Do we want to think of a metric that is stand alone? - not just for comparisons

@@

- draft methods section of the paper
- draft data example section of paper
- draft discussion section of paper
- draft appendices

>>>>

**Sandia**

- Memo about full time

@@

- What do you think of the new version of the plot that I created?
- Should we schedule my oral prelim, or should we keep waiting until I get closer to finishing the paper?
- What names should I give to the diagnostic plots?
- Could you help me with the interpretation of the default LIME explanations?
- Metrics:
    - MSEE (mean squared explanation error?) versus locality metric which would need to be computed via the perturbations
    - Do we want to think of a metric that is stand alone? - not just for comparisons

**Graphics Group**

- Did you have any resources for gganimate? (check out my slides so far)
- Treats for tomorrow?

@@

- draft paper
